Measurement Bias from Address Aliasing

### 2014-08-12 paper.tex
Add missing punctuation
Minor changes
Add core2 results graphic in introduction
Might be a good idea

@@

We also have to ensure we are not affected by measurement bias beyond what we are actually trying to observe, and in general follow best practices on gathering data~\cite{Mytkowicz:2009:WrongData}.
Most importantly, this means keeping the memory address space under control.
For security reasons, addresses of stack, heap and dynamic libraries are often randomized at load time, a technique known as \emph{Address Space Layout Randomization}~\cite{Pax:ASLR,Bhatkar:AddressObfuscation}. 
By disabling ASLR, we are able to execute the same program multiple times with identical virtual address spaces.
All experiments are done on a dedicated machine under minimal load, with \emph{frequency scaling} disabled to keep the CPU's clock speed fixed.
Finally, we disable \emph{Hyper-threading}, which reduces the possibility for resource contention between threads.

@@

% Large plot of cycle count for two 4K stack sections.
\pgfplotstableread{bin/micro-kernel-cycles.dat}{\stackoffsettable}
\begin{figure*}[t]
  \begin{tikzpicture}
    \begin{axis}[
        width = \textwidth,
        height = 6cm,
        font = \footnotesize,
        xlabel=Bytes added to environment,
        ylabel=Cycles,
        domain = 0:8192,
        xtick = {0,1024,...,8192},
        xmin = 0,
        xmax = 8192,
        cycle list name = exotic
      ]
      \addplot[ycomb] table[x expr = \thisrowno{0}*16, y = cycles:u] \stackoffsettable ;
    \end{axis}
  \end{tikzpicture}
  \caption{Bias from environment size for microkernel. Measured average of 10 cycle count samples for 512 different environments. Spikes show aliasing case, occurring once for each 4K period}
  \label{fig:envbias}
\end{figure*}

>>>>

\pgfplotstableread{bin/microkernel-cycles-core2.dat}{\microkernelcoretwotable}

\begin{figure}[t]
\begin{minipage}[t]{0.40\textwidth}
  \vspace{3mm}
  \begin{lstlisting}[frame=tb] %[frame=single]
  static int i, j, k;
  int main() {
      int g = 0, inc = 1;
      for (; g < 65536; g++) {
          i += inc;
          j += inc;
          k += inc;
      }
      return 0;
  }
  \end{lstlisting}
\end{minipage}
%\hfill
\begin{minipage}[t]{0.55\textwidth}
  \begin{flushleft}
    %\fbox{
    \begin{tikzpicture}
      \begin{axis}[
          width = 7.8cm,
          height = 4.5cm,
          font = \footnotesize,
          xlabel=Bytes added to environment,
          ylabel=Cycles,
          domain = 0:4096,
          xtick = {0,1024,...,4096},
          xmin = 0,
          xmax = 4096,
          cycle list name = exotic
        ]
        \addplot[ycomb] table[x expr = \thisrowno{0}*16, y = cycles:u] \microkernelcoretwotable ;
      \end{axis}
    \end{tikzpicture}
    %}
  \end{flushleft}
\end{minipage}
\label{fig:motivation}
\caption{Microkernel first presented in~\cite{Mytkowicz:2009:WrongData}, showing bias to environment size}
\end{figure}

@@

We also have to ensure we are not affected by measurement bias beyond what we are actually trying to observe, and in general follow best practices on gathering data~\cite{Mytkowicz:2009:WrongData}.
Most importantly, this means keeping the memory address space under control.
For security reasons, addresses of stack, heap and dynamic libraries are often randomized at load time, a technique known as \emph{Address Space Layout Randomization}~\cite{Pax:ASLR,Bhatkar:AddressObfuscation}. 
By disabling ASLR, we are able to execute the same program multiple times with identical virtual address spaces.
All experiments are done on a dedicated machine under minimal load, with \emph{frequency scaling} disabled to keep the CPU's clock speed fixed.
Finally, we disable \emph{Hyper-threading}, which reduces the possibility for resource contention between threads. Also some PMU events require HT to be turned off, or are inaccurate with HT.

@@

% Large plot of cycle count for two 4K stack sections.
\pgfplotstableread{bin/micro-kernel-cycles.dat}{\stackoffsettable}
\begin{figure*}[t]
  \begin{tikzpicture}
    \begin{axis}[
        width = \textwidth,
        height = 6cm,
        font = \footnotesize,
        xlabel=Bytes added to environment,
        ylabel=Cycles,
        domain = 0:8192,
        xtick = {0,1024,...,8192},
        xmin = 0,
        xmax = 8192,
        cycle list name = exotic
      ]
      \addplot[ycomb] table[x expr = \thisrowno{0}*16, y = cycles:u] \stackoffsettable ;
    \end{axis}
  \end{tikzpicture}
  \caption{Bias from environment size for microkernel. Measured average of 10 cycle count samples for 512 different environments. Spikes show aliasing case, occurring once for each 4K period.}
  \label{fig:envbias}
\end{figure*}
